A Standard for the Scholarly Citation of Archaeological Data: Supplementary Information

### 2017-08-21 analysis/paper/paper.Rmd
resolve merge conflict
simple scraping google scholar isn't possible, and there's no API

>>>>

```{r eval=FALSE}
# can we scrape google scholar for citation data?
# no, they are very sensitive to robots!

base_url <- "https://scholar.google.com/scholar?q="
doi <- dc_arch$doi
the_url <- paste0(base_url,doi)

# output storage
title_of_citing_item <-  vector("list", length(the_url))
title_of_no_items <- vector("list", length(the_url))

for(i in seq_along(the_url)){

library(rvest) 
the_content <- httr::GET(the_url[[i]],
                         user_agent(paste0(sample(letters[1:10]), collapse = "")))
the_content <- read_html(the_content)

title_of_citing_item[[i]] <- 
the_content %>% 
html_nodes(".gs_rt a") %>%
  html_text()

title_of_no_items[[i]] <- 
the_content %>% 
html_nodes("p") %>%
  html_text()

print(paste0(i, " ", title_of_citing_item[[i]], " ", title_of_no_items[[i]]))
Sys.sleep(sample(10, 1) * 0.5)

}

saveRDS(title_of_citing_item, "../data/raw_data/title_of_citing_item.rds")
saveRDS(title_of_no_items, "../data/raw_data/title_of_no_items.rds")

# there are none?
idx <- unlist(map(title_of_citing_item, ~!identical(.x, character(0))))
sum(idx)
title_of_citing_item[idx]

title_of_no_items

idx <- unlist(map(title_of_no_items, ~!identical(.x, character(0))))
sum(idx)
title_of_no_items[idx]

```{r eval = FALSE}
# This also doesn't work
require(RSelenium)

# vignette("RSelenium-docker", package = "RSelenium")

# docker run -d -p 4445:4444 selenium/standalone-firefox:2.53.0
# docker-machine ip
remDr <- remoteDriver(remoteServerAddr = "192.168.99.100",
                      port = 4445L)

base_url <- "https://scholar.google.com/scholar?q="
doi <- dc_arch$doi
the_url <- paste0(base_url,doi)

remDr$navigate(the_url[i])

remDr$getPageSource() %>% 
  unlist() %>% 
  read_html() %>% 
  html_nodes(".gs_rt a") %>%
  html_text()

remDr$getPageSource() %>% 
  unlist() %>% 
  read_html() %>% 
  html_nodes(".gs_med") %>%
  html_text()

remDr$getPageSource() %>% 
  unlist() %>% 
  read_html() %>% 
  html_nodes("p") %>%
  html_text()
